The Hot Hand Fallacy in Call of Duty Search and Destroy

### 2022-08-26 paper/paper.tex
render Two
thursday morning review

\author{
    Person One
   \\
     \\
   \\
  \texttt{\href{mailto:personone@domain.com}{\nolinkurl{personone@domain.com}}} \\
   \And
    Person two
   \\
     \\
   \\
  \texttt{\href{mailto:persontwo@domain.com}{\nolinkurl{persontwo@domain.com}}} \\
  }

@@

\usepackage{longtable}
\usepackage{amsmath}
\begin{document}
\maketitle

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  One team eliminates all members of the other team prior to a bomb
  plant. (Eliminating team wins.)
\item
  The offensive team eliminates all members of the defensive team after
  a bomb plant. (Offense wins.)
\item
  The defense defuses the bomb after a bomb plant.\footnote{Often the
    defensive team will try to eliminate all team members prior to
    making the defuse, but in some cases, they may try to ``ninja''
    defuse.} (Defense wins.)
\item
  The offense does not make a plant by the time the round timer ends.
  (Defense wins.)
\end{enumerate}

@@

We note that SnD is not the only game mode played in competitive
CoD.\footnote{Hardpoint has been played as the first and fourth maps in
  a matchup. The variant for the third map was Domination in the 2020
  season, and Control in the 2021 and 2022 seasons.} Teams play in a
head-to-head, best-of-five format, where SnD is always played as the
second and fifth game modes. The best-of-five matchup could also be
called a ``series'', but since we analyze only the SnD games, we refer
to the SnD games as series.

@@

CoD has roughly gone through three eras of professional gaming: (1)
Major League Gaming (MLG) tournaments prior to 2016; (2) the CoD World
League (CWL), initiated in 2016; and (3) the 12-franchise CoD League
(CDL), operating since 2020. The CDL has completed three year-long
``seasons'' as of August 2022.\footnote{CoD is fairly unique compared to
  other esports in that it runs on an annual lifecycle, with releases
  coming in the late fall. A new game under the same brand---Call of
  Duty---is published every year by a rotating set of developers. Each
  new game bears resemblance to past ones, often introducing relatively
  small variations (``improvements'') to graphics, game modes, and other
  facets of gameplay. During the CDL era, the games released have been
  Modern Warfare (2020), Cold War (2021) and Vanguard (2022).}

The data set consists of all SnD matches played in major tournaments and
qualifiers during the CDL era, totaling 7,792 rounds across 852
series.\footnote{288 of the series occur in major tournaments, which are
  considered to be more competitive than the qualifiers since they are
  played in person (COVID-permitting), eliminating randomness due to
  online latency and ping. The qualifiers are played online.} Data has
been collected in spreadsheets by community member
``IOUTurtle''.\footnote{Raw data: \url{https://linktr.ee/CDLArchive}.
  Author: \url{https://twitter.com/IOUTurtle}. Our clean data can be
  found at
  \url{https://github.com/tonyelhabr/fps_round_games/blob/master/data/cod_rounds.csv}.}

6-0 sweeps make up 4.7\% of all series, while 6-5 series make up 23.7\%
of series. The observed offensive round win percentage across all rounds
is \(\bar{\tau}_O\) = 47.8\%.\footnote{Offensive round win percentage
  has been nearly constant across the three games during the CDL era: 1.
  47.2\% in MW (2020) 2. 47.9\% in Cold War (2021) 3. 48.1\% in Vanguard
  (2022)} Table \ref{tbl:o-win-prop-by-series-state} shows offensive
round win percentages by series ``state'', i.e.~the number of round wins
by each team prior to an upcoming round. Offensive round win percentage
is not quite constant, although never veers more than 10\% from
\(\bar{\tau}_O\).

@@

At tournaments, higher-seeded (``better'') teams choose whether they
want to start on offense in the SnD series, played as the second or
fifth game mode of the best-of-five matchup. Their opponent is assigned
to start on offense in the SnD slot not chosen.\footnote{Anecdotally,
  the higher-seeded teams tend to choose to play defense in the first
  round of the SnD series played as the second game mode in the
  best-of-five matchup, although this choice is not consistent across
  teams, or even with the same team over time.} Outside of tournaments,
teams all play each other twice throughout the season, constituting
qualifiers. Each team gets to play the higher-seeded role once in their
head-to-head matchups with a given team, despite their win-loss records.
Overall, we can argue that potential bias due to stronger teams playing
defense---or, offense, if offense happens to be generally advantageous
for a given map---is very minimal.

@@

The concept of momentum goes hand-in-hand with a discussion of the
nature of series outcomes.\footnote{We often use ``streaks'' and
  momentum interchangeably, but as Steeger et al.~((2021)) note,
  momentum implies dependence between events, whereas streaking does
  not.} Two opposing fallacies are observed in the context of momentum:
the ``gambler's fallacy'' (negative recency) and the ``hot hand
fallacy'' (positive recency). Per Ayton et al. (2004), negative recency
is ``the belief that, for random events, runs of a particular outcome
\ldots{} will be balanced by a tendency for the opposite outcome'',
while positive recency is the expectation of observing future results
that match recent results.

@@

Other research has borrowed techniques from the field of quality
control, such as identifying unlikely sequences of events with the
Wald-Wolfowitz runs test (Peel and Clauset 2015, Steeger et al.~2021).
Peel and Clauset found no evidence for unlikely sequences of scoring
events in the NHL, College Football (CFB), and National Football League
(NFL), but did in the NBA. As a check on their entropy approach to
momentum identification, Steeger et al.~found several NHL teams with
sequence of wins in the 2018-2019 regular season that violated the
Wald-Wolfowitz null hypothesis.

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Both have economic aspects that can create clear advantages for one
  team in a round, given how prior rounds played out. CoD has no such
  equivalent, except for perhaps ``score streaks'', which infrequently
  occur.
\item
  Teams play either offense or defense for many consecutive rounds. (The
  former has a 15-15-1 format and the latter uses a 12-12-1 format.) On
  the other hand, teams in CoD SnD rotate roles every round, analogous
  to a 1-1-1-1-1-1-1 format for home advantage in best-of-seven series
  for professional sports like the MLB, NBA, and NHL.\footnote{1-1-1-1-1-1-1
    is not used today in these leagues, but it was at least once in
    each.} While theoretically one might be able to account for
  inter-round win percentage relationships in any kind of format, such
  as a 5-5-1, the rotation of team sides every round is convenient for
  convincing ourselves that rounds could reasonably be modeled as i.i.d.
  Bernoulli trials.
\item
  Both Counter-Strike and Valorant have overtime rules---team must win
  by two rounds---which can make end-of-series sequences difficult to
  model properly. CoD SnD does not have overtime rules.
\end{enumerate}

To our knowledge, there is no existing public statistical research on
the CoD SnD format, beyond descriptive analysis on social media. While
intra-round trends may be more directly applicable to teams looking for
an advantage on their competition, broader investigation of a concept
like the hot-hand fallacy in a sport where it has not yet been
invetigated---particularly one that is less subjected to factors that
may be difficult to control for, e.g.~weather---should be useful as a
precedent or supplement for future researchers.

@@

In a best-of-\(s\) format, assuming a constant round win probability
\(\phi\)\footnote{If \(\phi > 0.5\), we can say that this is the
  stronger team.} (where \(0 \leq \phi \leq 1\)) for one
team\footnote{\(\phi\) and other symbols are selected so as to reserve
  symbols like \(p\) for usage in other contexts without causing
  confusion for the reader. Upper-case symbol, e.g.~\(\Phi\), are
  consistently used in this paper to represent proportions, while
  lower-case symbols corresponding to upper-case symbols, e.g.~\(\phi\),
  are used to represent Bernoulli trial success rates. ``Hats'',
  e.g.~\(\hat{\Phi}\), are used to convey expectations, while bare
  symbols symbols convey observational data.}, the expected proportion
of series ending in \(r\) rounds (\(r \leq s\)) is given by Equation
\ref{eq:series-length}.

@@

For example, assuming \(\phi = 0.5\), the probability of a series ending
in nine rounds in CoD SnD, where \(s=11\), is

@@

in which \(\hat{\Phi}(r)\) and \(\Phi(r)\) represent the expected and
observed round win proportions respectively, and
\(R = [6, 7, 8, 9, 10, 11]\) for CoD SnD. The null hypothesis is that
the test statistic is chi-squared distributed, where the number of
degrees of freedom is \(\vert R \vert -1 = 5\) for Cod SnD. We reject
the null hypothesis if \(\chi^2 > \chi^2_{1-\alpha,\vert R \vert -1}\),
where \(\chi^2_{1-\alpha,\vert R \vert -1}\) is the chi-square critical
value with \(\vert R \vert -1\) degree of freedom and siginficance level
\(\alpha\).

@@

\begin{equation}\label{eq:pwr}
p_0(\text{win} | r) = p^{+|r}_0 = \begin{cases} 
  \frac{m}{r} & \text{team wins series}, \\ 
  \frac{r - m}{r} & \text{team loses series},
\end{cases}
\end{equation}

using \(m\) from Equation \ref{eq:m}.

As implied by MS's Theorem 1, we should expect the proportion of round
wins immediately following a streak of \(k\) rounds wins for a series
lasting \(r\) rounds, \(\hat{P}^{+|k,r}_{MS}\), to be strictly less than
\(p^{+|r}\).\footnote{Unfortunately, there does not exist a closed form
  representation for the expected value of \(\hat{P}^{+|k,r}_{MS}\) for
  \(k > 1\). Nonetheless, one may run simulations to estimate the
  expected value, as we choose to do. We have adapted the code from Vafa
  (2017), which implements MS's framework (2018).}

Although one might be tempted to mirror the equal proportions hypothesis
testing performed by MS, our context is fundamentally different from
that of MS, who focus on longitudinal data in controlled settings,
unaffected by opposition.\footnote{GVT also perform statistical tests on
  shots from players in live games, i.e.~``observational'' data, but
  they note that their findings are likely affected player shot
  selection in the face of defensive strategy by the opposing team.} The
number of trials is fixed in their experimental designs, but in CoD SnD,
the number of rounds played is determined as a function of the max
number of possible rounds (\(s\)) and whether or not the team wins the
series. The Bernoulli trial success probability, i.e.~single round win
percentage in CoD SnD, is not independent of the opponent. Consequently,
a statistical test of the difference in \(\hat{P}^{+|k,r}\) and
\(\hat{P}^{-|kr}\), as performed by MS to evaluate their hypothesis
regarding post-streak success rate, is not completely appropriate,
although useful as a reference.

@@

\begin{equation}\label{eq:pwkr}
p_0(\text{win} | k, r) = p^{+|k,r}_0 = \begin{cases}
  \frac{m - k}{r - k} & \text{team wins series}, \\
  \frac{s - m - k}{r - k} & \text{team loses series},
\end{cases}
\end{equation}

using \(m\) from Equation \ref{eq:m}.

@@

\begin{equation}\label{eq:binom}
\Pr(r^w) = {\binom {r}{r^+}} \omega^{r^+}(1-\omega)^{r-r^+}.
\end{equation}

@@

and where \(N^\zeta\) and \(\hat{N}^\zeta\) are the observed and
expected number of sequences respectively. The null hypothesis is that
\(z\) is normally distributed. If \(z > +z_{(1-\alpha)/2}\) or
\(z < -z_{(1-\alpha)/2}\) for critical values at a significance level
\(\alpha\), we can reject the null hypothesis for such sequences and
build an argument in support of the hot hand effect.

@@

In Table \ref{tbl:ww-sequences}, the observed and expected count of
sequences, \(N^{\zeta r}\) and \(\hat{N}^{\zeta r}\) respectively, are
shown for sequences, \(\zeta(r)\), for which one can reject the
Wald-Wolfowitz null hypothesis, given probability of Bernoulli trial
success \(\phi = 0.575\),\footnote{If we used \(\phi = 0.5\), we would
  get the same exact seqeunces.} at a confidence level of
\(\alpha = 0.05\), for \(r \in [8, 9, 10]\). In addition to the 13
sequences shown, there are 12 additional sequences for \(r = 11\).

@@

For the sake of brevity, we did not account for offensive or defensive
role when considering win proportions during streaks. For example, it
would be interesting to look at whether the round win percentage is
higher after a streaks of three round wins when the team starts the
streak as the offensive team. This would mean that, in the round
immediately following the latest streak win, the streaking team would be
playing defense, where teams are slightly more likely to win on average.
On the other hand, streaks of three starting with an offensive round
win---theoretically, knowing that \(\bar{\tau}_O\) = 47.7\%, the
expected frequency is \(\bar{\tau}_O^2 (1 - \bar{\tau}_O) \approx\)
11.9\%---are likely to occur less frequently than such streaks starting
with a defensive win---\(\bar{\tau}_O (1 - \bar{\tau}_O)^2 \approx\)
13.0\%---so we would want to account for sample size differences.

@@

Further regarding future work, we have contacted the Twitter user
``R11stats'', who privately tracks in-round player
engagements.\footnote{\url{https://twitter.com/R11stats}} R11stats
expressed intent on making the data public, which would allow for
research into player-specific momentum. While it seems there is no
team-level hot hand effect in CoD SnD, perhaps there is with
eliminations performed by individual players.

@@

\leavevmode\vadjust pre{\hypertarget{ref-vafa2017}{}}%
Vafa, Keyon. 2017. {``Is the Hot Hand Fallacy a Fallacy?''}
\url{https://keyonvafa.github.io/hot-hand/}.

>>>>

\author{
    Person One
   \\
     \\
   \\
  \texttt{\href{mailto:personone@domain.com}{\nolinkurl{personone@domain.com}}} \\
   \And
    Person Two
   \\
     \\
   \\
  \texttt{\href{mailto:persontwo@domain.com}{\nolinkurl{persontwo@domain.com}}} \\
  }

@@

\usepackage{amsmath}
\begin{document}
\maketitle

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  One team eliminates all members of the other team prior to a bomb
  plant. (Eliminating team wins.)
\item
  The offensive team eliminates all members of the defensive team after
  a bomb plant. (Offense wins.)
\item
  The defense defuses the bomb after a bomb plant. (Defense wins.)
\item
  The offense does not make a plant by the time the round timer ends.
  (Defense wins.)
\end{enumerate}

@@

We note that SnD is not the only game mode played in competitive
CoD.\footnote{Hardpoint has been played as the first and fourth game
  modes in a matchup. The third game mode was Domination in the 2020
  season, and Control in the 2021 and 2022 seasons.} Teams play in a
head-to-head, best-of-five format, where SnD is always played as the
second and fifth game modes. The best-of-five matchup could also be
called a ``series'', but since we analyze only the SnD games, we refer
to the SnD games as series.

@@

The data set consists of all SnD matches played in major tournaments and
qualifiers during the past three years\footnote{CoD has roughly gone
  through three eras of professional gaming: (1) Major League Gaming
  (MLG) tournaments prior to 2016; (2) the CoD World League (CWL),
  initiated in 2016; and (3) the 12-franchise CoD League (CDL),
  operating since 2020. The CDL has completed three year-long
  ``seasons'' as of August 2022.

  CoD is fairly unique compared to other esports in that it runs on an
  annual lifecycle, with releases coming in the late fall. A new game
  under the same brand---Call of Duty---is published every year by a
  rotating set of developers. Each new game bears resemblance to past
  ones, often introducing relatively small variations (``improvements'')
  to graphics, game modes, and other facets of gameplay. During the CDL
  era, the games released have been Modern Warfare (2020), Cold War
  (2021) and Vanguard (2022).}, totaling 7,792 rounds across 852
series.\footnote{288 of the series occur in major tournaments, which are
  considered to be more competitive than the qualifiers since they are
  played in person (COVID-permitting), eliminating randomness due to
  online latency and ping. The qualifiers are played online.} Data has
been collected in spreadsheets by community member
``IOUTurtle''.\footnote{Raw data: \url{https://linktr.ee/CDLArchive}.
  Cleaned data:
  \url{https://github.com/\%7Bauthor\%7D/\%7Brepo\%7D/blob/master/data/\%7Bfile\%7D.csv}.}

Sweeps (6-0 series) make up 4.7\% of all series, while 6-5 series make
up 23.7\% of series. The observed offensive round win percentage across
all rounds is \(\bar{\tau}\) = 47.8\%.\footnote{Offensive round win
  percentage has been nearly constant across the three games during the
  CDL era: 1. 47.2\% in MW (2020) 2. 47.9\% in Cold War (2021) 3. 48.1\%
  in Vanguard (2022)} Table \ref{tbl:o-win-prop-by-series-state} shows
offensive round win percentages by series ``state'', i.e.~the number of
round wins by each team prior to an upcoming round. Offensive round win
percentage is not quite constant, although never veers more than 10\%
from \(\bar{\tau}\).

@@

The professional competition format balances the frequency with which
teams play offense or defense to start a series, to the extent possible.
Thus, win percentages in certain states are subjected to minimal
selection bias, i.e.~bias due to better teams playing defense more
frequently.\footnote{At tournaments, higher-seeded (``better'') teams
  choose whether they want to start on offense in the SnD series, played
  as the second or fifth game mode of the best-of-five matchup. Their
  opponent is assigned to start on offense in the SnD slot not chosen.
  Anecdotally, the better team tends to choose to play defense in the
  first round of the SnD series played as the second game mode in the
  best-of-five matchup, although this choice is not consistent across
  teams, or even with the same team over time.

  Outside of tournaments, teams all play each other twice throughout the
  season, constituting qualifiers. Each team gets to play the
  higher-seeded role once in their head-to-head matchups with a given
  team, despite their win-loss records.}

@@

The concept of momentum goes hand-in-hand with a discussion of the
nature of series outcomes.\footnote{We often use ``streaks'' and
  momentum interchangeably, but as Steeger et al. (2021) note, momentum
  implies dependence between events, whereas streaking does not.} Two
opposing fallacies are observed in the context of momentum: the
``gambler's fallacy'' (negative recency) and the ``hot hand fallacy''
(positive recency). Per Ayton et al. (2004), negative recency is ``the
belief that, for random events, runs of a particular outcome \ldots{}
will be balanced by a tendency for the opposite outcome'', while
positive recency is the expectation of observing future results that
match recent results.

@@

Other research has borrowed techniques from the field of quality
control, such as identifying unlikely sequences of events with the
Wald-Wolfowitz runs test (Peel and Clauset 2015, Steeger et al.~2021).
Peel and Clauset found no evidence for unlikely sequences of scoring
events in the NHL, College Football, and National Football League,
although did in the NBA. As a check on their entropy approach to
momentum identification, Steeger et al.~found several NHL teams with
sequences of wins in the 2018-2019 regular season that violated the
Wald-Wolfowitz null hypothesis.

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Both have economic aspects that can create clear advantages for one
  team in a round, given how prior rounds played out. CoD has no such
  equivalent, except for perhaps ``score streaks'', which infrequently
  occur.
\item
  Teams play either offense or defense for many consecutive rounds. (The
  former has a 15-15-1 format and the latter uses a 12-12-1 format.) On
  the other hand, teams in CoD SnD rotate roles every round, analogous
  to a 1-1-1-1-1-1-1 format for home advantage in best-of-seven series
  for professional sports like the MLB, NBA, and NHL.\footnote{1-1-1-1-1-1-1
    is not used today in these leagues, but it was at least once in
    each.} While theoretically one might be able to account for
  inter-round win percentage relationships in any kind of format, such
  as a 5-5-1, the rotation of team sides every round is convenient for
  convincing ourselves that rounds could reasonably be modeled as i.i.d.
  Bernoulli trials.
\item
  Both Counter-Strike and Valorant have overtime rules---a team must win
  by two rounds---which can make end-of-series sequences difficult to
  model properly. CoD SnD does not have overtime rules.
\end{enumerate}

To our knowledge, there is no existing public statistical research on
the CoD SnD format, beyond descriptive analysis on social media. While
intra-round trends may be more directly applicable to teams looking for
an advantage on their competition, broader investigation of a concept
like the hot-hand fallacy in a sport where it has not yet been
invetigated---particularly one that is less subjected to factors that
may be difficult to control for, e.g.~weather---should be useful as an
inspiration for future researchers.

@@

In a best-of-\(s\) format, assuming a constant round win probability
\(\phi\) (where \(0 \leq \phi \leq 1\))\footnote{If \(\phi > 0.5\), we
  can say that this is the stronger team.} for one team\footnote{\(\phi\)
  and other symbols are selected so as to reserve symbols like \(p\) for
  usage in other contexts without causing confusion for the reader.
  Upper-case symbol, e.g.~\(\Phi\), are consistently used in this paper
  to represent proportions, while lower-case symbols corresponding to
  upper-case symbols, e.g.~\(\phi\), are used to represent Bernoulli
  trial success rates. ``Hats'', e.g.~\(\hat{\Phi}\), are used to convey
  expectations, while bare symbols symbols convey observational data.},
the expected proportion of series ending in \(r\) rounds (\(r \leq s\))
is given by Equation \ref{eq:series-length}.

@@

For example, assuming \(\phi = 0.5\), the probability of a series ending
in exactly nine rounds in CoD SnD, where \(s=11\) (implying \(m=6\)), is

@@

in which \(\hat{\Phi}(r)\) and \(\Phi(r)\) represent the expected and
observed round win proportions respectively, and
\(R = [6, 7, 8, 9, 10, 11]\) for CoD SnD. The null hypothesis is that
the test statistic is chi-squared distributed, where the number of
degrees of freedom is \(\vert R \vert -1 = 5\) for Cod SnD.

@@

\begin{equation}\label{eq:pwr}
p_0(\text{win} | r) = p^{+|r}_0 := \begin{cases} 
  \frac{m}{r} & \text{team wins series}, \\ 
  \frac{r - m}{r} & \text{team loses series},
\end{cases}
\end{equation}

for \(r \in R\) and \(m\) from Equation \ref{eq:m}.

As implied by MS's Theorem 1, we should expect the proportion of round
wins immediately following a streak of \(k\) rounds wins for a series
lasting \(r\) rounds, \(\hat{P}^{+|k,r}_{MS}\), to be strictly less than
\(p^{+|r}\). Although one might be tempted to mirror the equal
proportions hypothesis testing performed by MS, our context is
fundamentally different from that of MS, who focus on longitudinal data
in controlled settings, unaffected by opposition.\footnote{GVT also
  perform statistical tests on shots from players in live games,
  i.e.~``observational'' data, but they note that their findings are
  likely affected by player shot selection in the face of defensive
  strategy by the opposing team.} The number of trials is fixed in their
experimental designs, but in CoD SnD, the number of rounds played is
determined as a function of the max number of possible rounds (\(s\))
and whether or not the team wins the series. The Bernoulli trial success
probability, i.e.~single round win percentage in CoD SnD, is not
independent of the opponent. Consequently, a statistical test of the
difference in \(\hat{P}^{+|k,r}\) and \(\hat{P}^{-|kr}\), as performed
by MS to evaluate their hypothesis regarding post-streak success rate,
is not completely appropriate, although useful as a reference.

@@

\begin{equation}\label{eq:pwkr}
p_0(\text{win} | k, r) = p^{+|k,r}_0 := \begin{cases}
  \frac{m - k}{r - k} & \text{team wins series}, \\
  \frac{s - m - k}{r - k} & \text{team loses series},
\end{cases}
\end{equation}

for \(r \in R\) and \(m\) from Equation \ref{eq:m}.

@@

\begin{equation}\label{eq:binom}
\binom {r}{r^+} \omega^{r^+}(1-\omega)^{r-r^+}.
\end{equation}

@@

and where \(N^\zeta\) and \(\hat{N}^\zeta\) are the observed and
expected number of sequences respectively. The null hypothesis is that
\(z\) is normally distributed. If \(z > +z_{(1-\alpha)/2}\) or
\(z < -z_{(1-\alpha)/2}\) at a significance level \(\alpha\), we can
reject the null hypothesis for such sequences and build an argument in
support of the hot hand effect.

@@

In Table \ref{tbl:ww-sequences}, the observed and expected count of
sequences, \(N^{\zeta r}\) and \(\hat{N}^{\zeta r}\) respectively, are
shown for sequences, \(\zeta(r)\), for which one can reject the
Wald-Wolfowitz null hypothesis, given probability of Bernoulli trial
success \(\phi = 0.575\),\footnote{If we used \(\phi = 0.5\), we would
  get the same exact sequences.} at a confidence level of
\(\alpha = 0.05\), for \(r \inf [8, 9, 10]\). In addition to the 13
sequences shown, there are 12 additional sequences for \(r = 11\).

@@

For the sake of brevity, we did not account for offensive or defensive
role when considering win proportions in the rounds immediately
following streaks. For example, it would be interesting to look at
whether the round win percentage is higher after a streaks of three
round wins when the team starts the streak as the offensive team. This
would mean that, in the round immediately following the last streak win,
the streaking team would be playing defense, where teams are slightly
more likely to win on average. On the other hand, streaks of three
starting with an offensive round win are less likely to occur than such
streaks starting with a defensive
win-\(\bar{\tau}^2 (1 - \bar{\tau}) \approx\) 11.9\% in the former case
and \(\bar{\tau} (1 - \bar{\tau})^2 \approx\) 13.0\% in the latter
case---so we would need to properly account for sample size differences.

@@

Further regarding future work, we have contacted the Twitter user
``R11stats'', who privately tracks in-round player engagements. R11stats
expressed intent on making the data public, which would allow for
research into player-specific momentum. While it seems there is no
team-level hot hand effect in CoD SnD, perhaps there is with
eliminations performed by individual players.

@@
